---
title: "Autograd: Automatic Differentiation"
author: "Daniel Falbel"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

> This document is an R translation for the [article with the same name](https://pytorch.org/tutorials/beginner/blitz/autograd_tutorial.html#sphx-glr-beginner-blitz-autograd-tutorial-py) 
> in PyTorch docs.

Central to all neural networks in `torch` is the autograd package. Let’s first briefly visit this, and we will then go to training our first neural network.

The `autograd` feature provides automatic differentiation for all operations on Tensors. It is a define-by-run framework, which means that your backprop is defined by how your code is run, and that every single iteration can be different.

Let us see this in more simple terms with some examples.

## Tensor

`tensor` is the central class of the package. If you set its attribute `$requires_grad` as `TRUE`, 
it starts to track all operations on it. When you finish your computation you can 
call `$backward()` and have all the gradients computed automatically. 
The gradient for this tensor will be accumulated into `$grad` attribute.

To stop a tensor from tracking history, you can call `$detach()` to detach it 
from the computation history, and to prevent future computation from being tracked.

To prevent tracking history (and using memory), you can also wrap the code block in with `with_no_grad()`. 
This can be particularly helpful when evaluating a model because the model may have
trainable parameters with `requires_grad=TRUE`, but for which we don’t need the gradients.

There’s one more class which is very important for autograd implementation - a `Function`.

`tensor` and `Function` are interconnected and build up an acyclic graph, that encodes
a complete history of computation. Each tensor has a `$grad_fn` attribute that references 
a `Function` that has created the `tensor` (except for Tensors created by the user - their `grad_fn` is `NULL`).

If you want to compute the derivatives, you can call `$backward()` on a `tensor`. 
If Tensor is a scalar (i.e. it holds a one element data), you don’t need to specify 
any arguments to backward(), however if it has more elements, you need to specify 
a gradient argument that is a `tensor` of matching shape.

```{r}
library(torch)
```

Create a tensor and set `requires_grad=TRUE` to track computation with it:

```{r}
x <- tch_ones(c(2,2), requires_grad = TRUE)
x
```

Do a tensor operation:

```{r}
y <- x + 2
y
```

`y` was created as a result of an operation so it has a `grad_fn`:

```{r, eval = FALSE}
y$grad_fn
```


