---
title: "Tensors"
author: "Daniel Falbel"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(torch)
```

In this article we will describe the `Tensors` API implemented by `torch`.
A `tensor` is a multi-dimensional matrix containing elements of a single data type.

Torch defines eight CPU tensor types and eight GPU tensor types:

```{r echo=FALSE}
knitr::kable(data.frame(
  "Data type" = c("32-bit floating point", "64-bit floating point", "16-bit floating point", "8-bit integer (unsigned)", "8-bit integer (signed)", "16-bit integer (signed)", "32-bit integer (signed)", "64-bit integer (signed)"),
  "dtype"= c("float32 or float", "float64 or double", "float16 or half", "uint8", "int8", "int16 or short", "int32 or int", "int64 or long"),	
  "CPU tensor" = c("FloatTensor", "DoubleTensor", "HalfTensor", "ByteTensor", "CharTensor", "ShortTensor", "IntTensor", "LongTensor"),
  "CUDA tensor" = paste0("CUDA", c("FloatTensor", "DoubleTensor", "HalfTensor", "ByteTensor", "CharTensor", "ShortTensor", "IntTensor", "LongTensor")), check.names = FALSE
))
```

## Tensor Creation

### From R

We can create new tensors from R objects using the `tensor` function.

When creating `tensor`s from R vector types we will use the following convertion table.
Character tensors are not implemented yet.

```{r, echo = FALSE}
knitr::kable(
  data.frame(
    "R Type" = c("Logical", "Integer", "Double", "Character"),
    "dtype" = c("uint8", "int", "float", "int8"),
    "Torch Type" = c("ByteTensor", "IntTensor", "FloatTensor", "CharTensor"),
    check.names = FALSE
  )
)
```

> **Note** By default we cast doubles to floats because we can achieve much better performance on GPU.

```{r}
# Vectors
x <- runif(5)
x
x_ten <- tensor(x)
x_ten

# Matrixes
x <- matrix(runif(4), ncol = 2)
x
x_ten <- tensor(x)
x_ten

# Arrays
x <- array(runif(8), dim = c(2,2,2))
x
x_ten <- tensor(x)
x_ten
```

###  Using a Factory Function

The following factory functions are available at the time of this writing:

* `tch_arange`: Returns a tensor with a sequence of integers,
* `tch_empty`: Returns a tensor with uninitialized values,
* `tch_eye`: Returns an identity matrix,
* `tch_full`: Returns a tensor filled with a single value,
* `tch_linspace`: Returns a tensor with values linearly spaced in some interval,
* `tch_logspace`: Returns a tensor with values logarithmically spaced in some interval,
* `tch_ones`: Returns a tensor filled with all ones,
* `tch_rand`: Returns a tensor filled with values drawn from a uniform distribution on [0, 1).
* `tch_randint`: Returns a tensor with integers randomly drawn from an interval,
* `tch_randn`: Returns a tensor filled with values drawn from a unit normal distribution,
* `tch_randperm`: Returns a tensor filled with a random permutation of integers in some interval,
* `tch_zeros`: Returns a tensor filled with all zeros.

For example we can create a tensor with:

```{r}
x <- tch_randn(c(2,2))
x
```

## Configuring Properties of the Tensor

There are 4 construction axis for a tensor, they are:

* The dtype, which controls the data type of the elements stored in the tensor,
* The layout, which is either strided (dense) or sparse,
* The device, which represents a compute device on which a tensor is stored (like a CPU or CUDA GPU),
* The requires_grad boolean to enable or disable gradient recording for a tensor,

If you are used to PyTorch in Python, these axes will sound very familiar. The allowed values for these axes at the moment are:

* For `dtype`: `uint8`, `int` or `int32`, `float` or `float32` and `double` or `float64`,
* For `layout`: `strided` or `dense`,
* For `device`: `cpu`, (no `cuda` support yet),
* For `requires_grad`: either `TRUE` or  `FALSE`.
